Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
results future work and stuff

@@

- Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parameterizable, meaning, a set of queries are all related and may be answered using a single QRM.  We plan to investigate this.

@@

>>>>

The largest limitation to our current work is the the QRR.  In order to efficiently answer new user questions the systems needs a large amount of user annotated queries.  However, a significant amount user interaction is required to understand the answer retrieval process.  By continuing to studying the methods of user data collection we plan to develop a model to support a unsupervised question resolution process.  This will increase the scalability and efficiency of the system.

Because each QRM may be treated as a function, we plan on leveraging previous work to allow new questions to be solved by connecting together several QRMs \cite{morpheus1, transformscout}.  This method would expand the types of queries that are answerable be the system.

@@

Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that an even higher number of those are parametrizable, meaning, a set of queries are all related and may be answered using a single QRM.  It is difficult to discover this property.  Previous work suggest techniques to find related queries but it will take a new method to discover parametrizable queries.

@@

In this paper we provide a discussion on a new type of question answering system that uses previously answered questions user.  We described our method of modelling a users question answering process and how we are able to discover semantically similar queries.

MORE
